---
title: "MongoPlot"
author: "JL"
date: "12/15/2018"
output: html_document
---

```{r setup, include=FALSE,echo=FALSE}
library(ggplot2)
library(dplyr)
library(maps)
library(ggmap)
library(mongolite)
library(lubridate)
library(gridExtra)
my_collection = mongo(collection = "cats", db = "Cats") # create connection, database and collection


```


`r my_collection$count()` Total cats 



### Test

```{r message=FALSE,warning=FALSE,echo=FALSE }
df <-
  my_collection$find(query = '{"name" : "Rye8", "lon" : { "$lt" : -90.26455 }, "lon" : { "$gt" : -90.30376 }, "lat" : { "$lt" : 38.64781 },"lat" : { "$gt" : 38.63027 },  "$or": [ { "activity": "Running" }, { "activity": "Bike" }, { "activity": "Walking" } ]}')

qmplot(lon, lat, data = df, maptype = "toner-lite", geom = "density2d", color = I("red"))+ stat_density2d(data = df, aes(x = lon, y = lat, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 16, geom = 'polygon')

qmplot(lon, lat, data = df, maptype = "toner-lite", geom = "point", color = I("red"))

